
\definecolor{lightgray}{gray}{0.85}
\definecolor{orange}{rgb}{ 0.95, 0.4, 0.2 }
\definecolor{lightblue}{rgb}{ 0.6, 0.7, 1.0 }

\newcommand{\PriorityLow}		{Low}
\newcommand{\PriorityNormal}	{Normal}
\newcommand{\PriorityHigh}		{High}

\newcommand{\issue}[4] {
						
						\begin{tabularx}{1\textwidth}{
											|r@{ }
											>{\setlength\hsize{1\hsize}
												\raggedright\arraybackslash}X| }
						\hline
						\colorbox{orange}{Registered at:}	& \texttt{#1}	\\

						\colorbox{green}{Solved at:}		& \texttt{#2}	\\
						
						\colorbox{lightblue}{Priority: }	& \texttt{#3}	\\

						\colorbox{lightgray}{Description:}	& #4			\\
						\hline
						\end{tabularx}
						}


\section{TODOs and FIXMEs}

\subsection{Unresolved issues}

	\begin{enumerate}

	\item	\issue{Tue Feb 26 10:12:29 CET 2013}
					{}
					{\PriorityLow}
		{
			Description of the issue.
		}

	\end{enumerate}

	
\subsection{Resolved issues}

	\begin{enumerate}

	\item	\issue{Wed Feb  6 09:13:17 CET 2013}
					{Wed Feb 27 10:32:59 CET 2013}
					{\PriorityNormal}
		{
			Description of the solved issue.
		}

	\end{enumerate}
	
\subsection{How to Eliminate Fifty Per Cent of (Tour Business) Worries}

	Advices from Dale Carnegie.

	\begin{description}
	\item[Question 1:] What is the problem?

		("In the old days we used to spend an hour or two in a worried
		conference without anyone's knowing
		specifically and concretely what the real problem was. We used to work
		ourselves into a lather
		discussing our troubles without ever troubling to write out specifically
		what our problem was.)

	\item[Question 2:] What is the cause of the problem?

		("As I look back over my career, I am appalled at the wasted hours I
		have spent in worried
		conferences without ever trying to find out clearly the conditions which
		lay at the root of the
		problem.)

	\item[Question 3:] What are all possible solutions of the problem?

		("In the old days, one man in the conference would suggest one solution.
		Someone else would argue
		with him. Tempers would flare. We would often get clear off the subject,
		and at the end of the
		conference no one would have written down all the various things we
		could do to attack the problem.)

	\item[Question 4:] What solution do you suggest?

		("I used to go into a conference with a man who had spent hours worrying
		about a situation and going
		around in circles without ever once thinking through all possible
		solutions and then writing down:
		'This is the solution I recommend.')

	\end{description}

